\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Rahat Khandokar} \\ \vspace{1pt}
    \small 917-495-6045 $|$ \href{mailto:x@x.com}{\underline{Rahatkhandokar5@gmail.com}} $|$ 
    \href{https://linkedin.com/in/rahatkhandokar}{\underline{linkedin.com/in/rahatkhandokar/}} $|$
    \href{https://github.com/...}{\underline{github.com/Rahatk1}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hunter College}{Manhattan, NY}
      {Bachelor of Arts in Computer Science, Minor in Mathematics}{Aug. 2021 -- Expected May 2025}
    % \resumeSubheading
    %   {John Bowne High School }{Queens, NY}
    %   {High School Diploma}{September. 2017 -- June 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Teacher}{June 2021 -- January 2022}
      {Kumon North America, Inc}{Queens, NY}
      \resumeItemListStart
        \resumeItem{Coordinated a classroom of 40 kids, ranging from grades K-12. }
        \resumeItem{Taught students English and Math, graded homework and classwork while administering daily problem sets for students.}
        % \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Google Code Next Engineering Student}{Sep. 2020 -- June 2021}
      {Google}{Manhattan, NY}
      \resumeItemListStart
        \resumeItem{Attended weekly workshops led by top google engineers which taught computer science concepts such as Systems and Networks, Cyber Security and DevOps.
  }
        \resumeItem{Participated in 4 different bootcamp activities for career development and technical skills}
        \resumeItem{Created 5 projects and a website that was viewed by Google Software engineers and product managers. }
    \resumeItemListEnd

    \resumeSubheading
      {Front End Student}{July 2019 -- September 2019}
      {All Star Code}{Manhattan, NY}
      \resumeItemListStart
        \resumeItem{36 hours/week of JavaScript, HTML, and CSS exposure and implementation.}
        \resumeItem{Administered and led 25 small projects and websites using P5.JS and PixiJS.  }
        \resumeItem{Launched an app called Truck Tracker that allows users to locate food trucks near their location and look at the food truck’s menu.}
        \resumeItem{Created Truck Tracker using 3 languages (JavaScript, HTML and CSS) and implemented Google maps API and Google Firebase.}
        \resumeItem{Mentored by a senior product manager at Amazon, Learned about product management within the technology sector.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
   
      \resumeProjectHeading
          {\textbf{ASLearn} $|$ \emph{JavaScript, HTML, CSS}}{February 2022 -- March 2022}
          \resumeItemListStart
            \resumeItem{Programmed an application that allows users to learn American Sign Language
 while creating awareness for the deaf community.}
             \resumeItem{Implemented Javascript to build an ASL memory game which allows users to test their knowledge of sign language by taking random generated quizzes consisting of phrases and images.
               \resumeItem{Assisted designing 26 alphabetical letters using Adobe Photoshop and Procreate which was then implemented in the application.}
             }

          \resumeItemListEnd
           \resumeProjectHeading
          {\textbf{Portfolio} $|$ \emph{JavaScript, Firebase, HTML, CSS}}{January 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a personal website that displays my portfolio.}
          \resumeItemListEnd
              \resumeItemListStart
           \resumeItem{Users are able to download resume and use contact form to reach out.}
          \resumeItemListEnd
                \resumeProjectHeading
          {\textbf{Jump Mario} $|$ \emph{Python, HTML, CSS}}{February 2022 -- February 2022}
          \resumeItemListStart
            \resumeItem{Architected a game where the user used navigation keys to control Mario's movement and not allow him to hit any pole or obstacle that comes at him.  }
          \resumeItemListEnd
           \resumeItemListStart
            \resumeItem{Won Number 1 within a class of 45 for the fastest developed game within 1 hour.  }
          \resumeItemListEnd
          
          
          
          
      \resumeProjectHeading
          {\textbf{Truck Tracker} $|$ \emph{Google Maps API, JavaScript, HTML, CSS}}{August 2019 -- August 2019}
          \resumeItemListStart
            \resumeItem{Developed an application that shows food trucks near Manhattan NY}
            \resumeItem{Used the Google Maps API to get user location and list nearest Food truck with menus and prices.}
            \resumeItem{Collaborated with Medidata Solutions employee's to suggest features and get feedback about the web application.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, HTML/CSS, LaTeX} \\
    %  \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Google Cloud Platform, VS Code, Visual Studio} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Folium}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
